---
title: Forcasting In R
author: Ross
date: '2017-06-25'
slug: forcasting-in-r
categories:
  - R
  - Forecast
tags: []
---

Just some notes, findings and tips from my workshop.

Never knew what `%%` does. It gives the mode...

```{r}
7 %% 2

```


*Exponetial smoothing*

Straight line through the data....

`forcast` packge defaults to Akaike's Information Criterion (AIC) for it's selection...


Some tools that my tutors made:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
invisible(library(forecast))
invisible(library(TStools))

```

```{r}
setwd("/Users/rosseji/Dropbox/TrendLock/ISF/forecasting with R/")
# Load the three time series, as before
ts1 <- ts(scan("ts1.txt"), start=c(2011,1), frequency=4)
ts2 <- ts(scan("ts2.txt"), start=c(2011,1), frequency=12)
ts3 <- ts(scan("ts3.txt"), start=c(2011,1), frequency=12)

# Let us store the time series to be explored in variable `y' so that we can  
# repeat the analysis easily with new data if needed.
y <- ts2

# First we plot the series to get a general impression
plot(y)


```

```{r}
# ----- Trend -----
# Let us look for trend in the data, by calculating the Centred Moving
# Average
cma <- cmav(y, outplot=1)
print(cma)

cmav(y, outplot=1, fill=T)

```

```{r}

#Seasonality
seasplot(ts2)

seasplot(ts1)


```

Addative vs Multiplicative

An argument in decompse. In the ts below we can that the seasonality grows as time goes on (ie the y components widens)

```{r}
plot(ts2)

```


Seeing internal trends... (like two peaks)

```{r}
seasplot(y,outplot=3)
```


Test in a moving average

Non-paramatric test don't assume norm dist and hence are closer to realistic data...

```{r}
coxstuart(cma)

```

Test seasonality

```{r}
seasplot(cma)

```

```{r}
seasplot(ts2)

```


Instead of acf pacf tests?

```{r}
plot(diff(ts2, 12))

```

```{r}
plot(diff(y, 12))
yd <- diff(y, 1)
plot(yd)
ydd <- plot(diff(yd, 12))
ydd
```